\LARGE \bf The Battle for Filter Supremacy: A Retrospective: The Movie: The Game: The Paper

### 2014-12-20 Report/project_report.tex
Minor changes. Still haven't found the problem yet.

Since $\Vec{H}_{f}^{(j)}$ has full column rank, $\Vec{A}$ has dimension $\left(2M_j - 3\right) \times 3$ and $\Vec{r}_o^{(j)}$ has dimension $\left(2M_j - 3\right) \times 1$.
Furthermore, because $\Vec{A}$ is semi-unitary, the covariance matrix of $\Vec{n}_o^{(j)}$ is given by $\Vec{R}_o = \sigma^2_{\text{im}}\Vec{A}^T\Vec{A} = \sigma^2_{\text{im}}\Vec{1}_{2M_j - 3}$.

>>>>

Since $\Vec{H}_{f}^{(j)}$ has full column rank, $\Vec{A}$ has dimension $2M_j \times \left(2M_j - 3\right)$ and $\Vec{r}_o^{(j)}$ has dimension $\left(2M_j - 3\right) \times 1$.
Furthermore, because $\Vec{A}$ is semi-unitary, the covariance matrix of $\Vec{n}_o^{(j)}$ is given by $\Vec{R}_o = \sigma^2_{\text{im}}\Vec{A}^T\Vec{A} = \sigma^2_{\text{im}}\Vec{1}_{2M_j - 3}$.
